Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-02-25 paper/paper1/ms.tex
Add references from @18ganesha and a few more

\subsection{MCMC}
We fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}. The model consists of a straight-line trend with a Gaussian absorption line.  It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.

@@

The sky fiber and target fiber have slightly different sizes and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.  On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength.  We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.  We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line residuals.  A few lines exhibit residuals which may arise from slight differences in the local atmospheric conditions between the target and sky fiber.

This refined sky-subtraction and all of our other standard pre-processing steps are implemented in a new open-source Python toolkit \texttt{muler} (Gully-Santiago \emph{et al.}, submitted).

@@

\begin{deluxetable*}{lcccccc}[!ht]
    \tablecaption{Equivalent Width \label{tab:ew_properties}}
    \tablehead{
        \colhead{Star Name} & \colhead{Date} & \colhead{ID} & \colhead{Observed Line Center Position} & \colhead{Intrinsic Line Center Position} & \colhead{Equivalent Width (\AA)}}
    \startdata
    HAT-P-67 & Aug 7, 2020 & & $10328.493\pm0.017$ & & $0.1607\pm0.0059$\\
    HAT-P-67 & Aug 8, 2020 & & $10345.007\pm0.019$ & & $0.1122\pm0.0068$\\
    HAT-P-67 & Aug 8, 2020 & & $10344.993^{+0.015}_{-0.016}$ & & $0.1064\pm0.0051$\\
    \enddata
\end{deluxetable*}

\begin{tabular}{lrrrlrll}
    \toprule
    date       & declination & exposure time & jd           & qidx   & ra        & star name                  & time     \\
    \midrule
    2020-04-28 & 44.763974   & 308.85        & 2.458968e+06 & 6437.0 & 17.106801 & HAT-P-67b\_IN\_1           & 06:10:31 \\
    2020-04-28 & 44.763643   & 308.85        & 2.458968e+06 & 6437.0 & 17.106878 & HAT-P-67b\_IN\_1           & 06:16:12 \\
    2020-04-28 & 44.763456   & 308.85        & 2.458968e+06 & 6437.0 & 17.106957 & HAT-P-67b\_IN\_1           & 06:21:53 \\
    2020-04-28 & 44.763237   & 308.85        & 2.458968e+06 & 6437.0 & 17.107029 & HAT-P-67b\_IN\_1           & 06:27:34 \\
    2020-04-28 & 44.763050   & 308.85        & 2.458968e+06 & 6437.0 & 17.107089 & HAT-P-67b\_IN\_1           & 06:33:15 \\
    2020-04-28 & 44.762969   & 308.85        & 2.458968e+06 & 6437.0 & 17.107158 & HAT-P-67b\_IN\_1           & 06:38:57 \\
    2020-04-28 & 44.762784   & 308.85        & 2.458968e+06 & 6437.0 & 17.107229 & HAT-P-67b\_IN\_1           & 06:44:38 \\
    2020-04-28 & 44.762775   & 308.85        & 2.458968e+06 & 6437.0 & 17.107301 & HAT-P-67b\_IN\_1           & 06:50:19 \\
    2020-04-28 & 44.762575   & 308.85        & 2.458968e+06 & 6437.0 & 17.107363 & HAT-P-67b\_IN\_1           & 06:56:00 \\
    2020-04-28 & 44.762322   & 308.85        & 2.458968e+06 & 6437.0 & 17.107427 & HAT-P-67b\_IN\_1           & 07:01:41 \\
    2020-04-28 & 44.762290   & 308.85        & 2.458968e+06 & 6437.0 & 17.107485 & HAT-P-67b\_IN\_1           & 07:07:22 \\
    2020-04-28 & 44.762212   & 308.85        & 2.458968e+06 & 6437.0 & 17.107541 & HAT-P-67b\_IN\_1           & 07:13:03 \\
    2020-04-28 & 44.762057   & 308.85        & 2.458968e+06 & 6437.0 & 17.107608 & HAT-P-67b\_IN\_1           & 07:18:44 \\
    2020-04-28 & 44.762013   & 308.85        & 2.458968e+06 & 6437.0 & 17.107669 & HAT-P-67b\_IN\_1           & 07:24:26 \\
    2020-05-22 & 44.765938   & 308.85        & 2.458992e+06 & 6587.0 & 17.106844 & HAT-P-67b\_IN\_2           & 04:41:05 \\
    2020-05-22 & 44.765694   & 308.85        & 2.458992e+06 & 6587.0 & 17.106916 & HAT-P-67b\_IN\_2           & 04:46:46 \\
    2020-05-22 & 44.765448   & 308.85        & 2.458992e+06 & 6587.0 & 17.106988 & HAT-P-67b\_IN\_2           & 04:52:27 \\
    2020-05-22 & 44.765338   & 308.85        & 2.458992e+06 & 6587.0 & 17.107057 & HAT-P-67b\_IN\_2           & 04:58:09 \\
    2020-05-22 & 44.765232   & 308.85        & 2.458992e+06 & 6587.0 & 17.107116 & HAT-P-67b\_IN\_2           & 05:03:50 \\
    2020-05-22 & 44.764945   & 308.85        & 2.458992e+06 & 6587.0 & 17.107198 & HAT-P-67b\_IN\_2           & 05:09:31 \\
    2020-05-22 & 44.764912   & 308.85        & 2.458992e+06 & 6587.0 & 17.107269 & HAT-P-67b\_IN\_2           & 05:15:12 \\
    2020-05-22 & 44.764767   & 308.85        & 2.458992e+06 & 6587.0 & 17.107347 & HAT-P-67b\_IN\_2           & 05:20:53 \\
    2020-05-22 & 44.764488   & 308.85        & 2.458992e+06 & 6587.0 & 17.107408 & HAT-P-67b\_IN\_2           & 05:26:34 \\
    2020-05-22 & 44.764364   & 308.85        & 2.458992e+06 & 6587.0 & 17.107473 & HAT-P-67b\_IN\_2           & 05:32:15 \\
    2020-05-22 & 44.764240   & 308.85        & 2.458992e+06 & 6587.0 & 17.107525 & HAT-P-67b\_IN\_2           & 05:37:57 \\
    2020-05-22 & 44.764128   & 308.85        & 2.458992e+06 & 6587.0 & 17.107601 & HAT-P-67b\_IN\_2           & 05:43:38 \\
    2020-05-22 & 44.764087   & 308.85        & 2.458992e+06 & 6587.0 & 17.107653 & HAT-P-67b\_IN\_2           & 05:49:19 \\
    2020-05-22 & 44.763816   & 308.85        & 2.458992e+06 & 6587.0 & 17.107728 & HAT-P-67b\_IN\_2           & 05:55:00 \\
    2020-06-15 & 44.768164   & 308.85        & 2.459016e+06 & 6938.0 & 17.106909 & HAT-P-67b\_IN\_3           & 03:13:19 \\
    2020-06-15 & 44.767792   & 308.85        & 2.459016e+06 & 6938.0 & 17.106979 & HAT-P-67b\_IN\_3           & 03:19:00 \\
    2020-06-15 & 44.767746   & 308.85        & 2.459016e+06 & 6938.0 & 17.107035 & HAT-P-67b\_IN\_3           & 03:24:41 \\
    2020-06-15 & 44.767580   & 308.85        & 2.459016e+06 & 6938.0 & 17.107103 & HAT-P-67b\_IN\_3           & 03:30:23 \\
    2020-06-15 & 44.767436   & 308.85        & 2.459016e+06 & 6938.0 & 17.107145 & HAT-P-67b\_IN\_3           & 03:36:04 \\
    2020-06-15 & 44.767252   & 308.85        & 2.459016e+06 & 6938.0 & 17.107246 & HAT-P-67b\_IN\_3           & 03:41:45 \\
    2020-06-15 & 44.767175   & 308.85        & 2.459016e+06 & 6938.0 & 17.107295 & HAT-P-67b\_IN\_3           & 03:47:26 \\
    2020-06-15 & 44.766835   & 308.85        & 2.459016e+06 & 6938.0 & 17.107368 & HAT-P-67b\_IN\_3           & 03:53:07 \\
    2020-06-15 & 44.766759   & 308.85        & 2.459016e+06 & 6938.0 & 17.107418 & HAT-P-67b\_IN\_3           & 03:58:48 \\
    2020-04-27 & 44.764544   & 308.85        & 2.458967e+06 & 6436.0 & 17.106775 & HAT-P-67b\_OUT\_1\_before1 & 06:29:11 \\
    2020-04-27 & 44.764240   & 308.85        & 2.458967e+06 & 6436.0 & 17.106827 & HAT-P-67b\_OUT\_1\_before1 & 06:35:03 \\
    2020-04-27 & 44.764141   & 308.85        & 2.458967e+06 & 6436.0 & 17.106900 & HAT-P-67b\_OUT\_1\_before1 & 06:40:55 \\
    2020-04-27 & 44.763873   & 308.85        & 2.458967e+06 & 6436.0 & 17.106974 & HAT-P-67b\_OUT\_1\_before1 & 06:46:47 \\
    2020-04-29 & 44.764930   & 308.85        & 2.458969e+06 & 6438.0 & 17.106673 & HAT-P-67b\_OUT\_1\_after1  & 06:34:20 \\
    2020-04-29 & 44.764731   & 308.85        & 2.458969e+06 & 6438.0 & 17.106749 & HAT-P-67b\_OUT\_1\_after1  & 06:40:01 \\
    2020-04-29 & 44.764633   & 308.85        & 2.458969e+06 & 6438.0 & 17.106817 & HAT-P-67b\_OUT\_1\_after1  & 06:45:42 \\
    2020-04-29 & 44.764531   & 308.85        & 2.458969e+06 & 6438.0 & 17.106878 & HAT-P-67b\_OUT\_1\_after1  & 06:51:23 \\
    2020-05-20 & 44.782750   & 308.85        & 2.458990e+06 & 6599.0 & 17.107624 & HAT-P-67b\_OUT\_2\_before2 & 10:43:31 \\
    2020-05-20 & 44.781504   & 308.85        & 2.458990e+06 & 6599.0 & 17.107668 & HAT-P-67b\_OUT\_2\_before2 & 10:49:12 \\
    2020-05-20 & 44.780211   & 308.85        & 2.458990e+06 & 6599.0 & 17.107719 & HAT-P-67b\_OUT\_2\_before2 & 10:54:53 \\
    2020-05-20 & 44.779210   & 308.85        & 2.458990e+06 & 6599.0 & 17.107778 & HAT-P-67b\_OUT\_2\_before2 & 11:00:34 \\
    2020-05-21 & 44.782995   & 308.85        & 2.458991e+06 & 6588.0 & 17.107695 & HAT-P-67b\_OUT\_2\_before1 & 10:23:05 \\
    2020-05-21 & 44.781573   & 308.85        & 2.458991e+06 & 6588.0 & 17.107731 & HAT-P-67b\_OUT\_2\_before1 & 10:28:46 \\
    2020-05-21 & 44.780368   & 308.85        & 2.458991e+06 & 6588.0 & 17.107773 & HAT-P-67b\_OUT\_2\_before1 & 10:34:28 \\
    2020-05-21 & 44.779170   & 308.85        & 2.458991e+06 & 6588.0 & 17.107810 & HAT-P-67b\_OUT\_2\_before1 & 10:40:09 \\
    2020-05-23 & 44.783203   & 308.85        & 2.458993e+06 & 6589.0 & 17.107654 & HAT-P-67b\_OUT\_2\_after1  & 10:16:00 \\
    2020-05-23 & 44.781895   & 308.85        & 2.458993e+06 & 6589.0 & 17.107688 & HAT-P-67b\_OUT\_2\_after1  & 10:21:41 \\
    2020-05-23 & 44.780749   & 308.85        & 2.458993e+06 & 6589.0 & 17.107718 & HAT-P-67b\_OUT\_2\_after1  & 10:27:22 \\
    2020-05-23 & 44.779639   & 308.85        & 2.458993e+06 & 6589.0 & 17.107763 & HAT-P-67b\_OUT\_2\_after1  & 10:33:04 \\
    2020-05-24 & 44.782834   & 308.85        & 2.458994e+06 & 6600.0 & 17.107668 & HAT-P-67b\_OUT\_2\_after2  & 10:22:14 \\
    2020-05-24 & 44.781654   & 308.85        & 2.458994e+06 & 6600.0 & 17.107708 & HAT-P-67b\_OUT\_2\_after2  & 10:27:55 \\
    2020-05-24 & 44.780276   & 308.85        & 2.458994e+06 & 6600.0 & 17.107744 & HAT-P-67b\_OUT\_2\_after2  & 10:33:36 \\
    2020-05-24 & 44.779039   & 308.85        & 2.458994e+06 & 6600.0 & 17.107789 & HAT-P-67b\_OUT\_2\_after2  & 10:39:17 \\
    2020-06-13 & 44.785061   & 308.85        & 2.459014e+06 & 6941.0 & 17.107689 & HAT-P-67b\_OUT\_3\_before2 & 09:13:57 \\
    2020-06-13 & 44.783754   & 308.85        & 2.459014e+06 & 6941.0 & 17.107743 & HAT-P-67b\_OUT\_3\_before2 & 09:19:38 \\
    2020-06-13 & 44.782668   & 308.85        & 2.459014e+06 & 6941.0 & 17.107795 & HAT-P-67b\_OUT\_3\_before2 & 09:25:19 \\
    2020-06-14 & 44.785228   & 308.85        & 2.459015e+06 & 6939.0 & 17.107679 & HAT-P-67b\_OUT\_3\_before1 & 09:08:28 \\
    2020-06-14 & 44.783951   & 308.85        & 2.459015e+06 & 6939.0 & 17.107713 & HAT-P-67b\_OUT\_3\_before1 & 09:14:09 \\
    2020-06-14 & 44.782721   & 308.85        & 2.459015e+06 & 6939.0 & 17.107767 & HAT-P-67b\_OUT\_3\_before1 & 09:19:50 \\
    2020-06-14 & 44.781659   & 308.85        & 2.459015e+06 & 6939.0 & 17.107823 & HAT-P-67b\_OUT\_3\_before1 & 09:25:32 \\
    2020-06-15 & 44.783524   & 308.85        & 2.459016e+06 & 6943.0 & 17.107765 & HAT-P-67b\_OUT\_same3      & 08:59:57 \\
    2020-06-15 & 44.782226   & 308.85        & 2.459016e+06 & 6943.0 & 17.107803 & HAT-P-67b\_OUT\_same3      & 09:05:39 \\
    2020-06-15 & 44.780921   & 308.85        & 2.459016e+06 & 6943.0 & 17.107841 & HAT-P-67b\_OUT\_same3      & 09:11:20 \\
    2020-06-15 & 44.779720   & 308.85        & 2.459016e+06 & 6943.0 & 17.107889 & HAT-P-67b\_OUT\_same3      & 09:17:01 \\
    2020-06-15 & 44.778571   & 308.85        & 2.459016e+06 & 6943.0 & 17.107938 & HAT-P-67b\_OUT\_same3      & 09:22:42 \\
    2020-06-15 & 44.777286   & 308.85        & 2.459016e+06 & 6943.0 & 17.108007 & HAT-P-67b\_OUT\_same3      & 09:28:23 \\
    2020-06-15 & 44.776196   & 308.85        & 2.459016e+06 & 6943.0 & 17.108044 & HAT-P-67b\_OUT\_same3      & 09:34:04 \\
    2020-06-15 & 44.774972   & 308.85        & 2.459016e+06 & 6943.0 & 17.108092 & HAT-P-67b\_OUT\_same3      & 09:39:45 \\
    2020-06-15 & 44.773796   & 308.85        & 2.459016e+06 & 6943.0 & 17.108157 & HAT-P-67b\_OUT\_same3      & 09:45:26 \\
    2020-06-16 & 44.785595   & 308.85        & 2.459017e+06 & 6940.0 & 17.107685 & HAT-P-67b\_OUT\_3\_after1  & 08:51:26 \\
    2020-06-16 & 44.784378   & 308.85        & 2.459017e+06 & 6940.0 & 17.107727 & HAT-P-67b\_OUT\_3\_after1  & 08:57:07 \\
    2020-06-16 & 44.783087   & 308.85        & 2.459017e+06 & 6940.0 & 17.107751 & HAT-P-67b\_OUT\_3\_after1  & 09:02:49 \\
    2020-06-16 & 44.781929   & 308.85        & 2.459017e+06 & 6940.0 & 17.107796 & HAT-P-67b\_OUT\_3\_after1  & 09:08:30 \\
    2020-06-18 & 44.785281   & 308.85        & 2.459019e+06 & 6942.0 & 17.107699 & HAT-P-67b\_OUT\_3\_after2  & 08:58:34 \\
    2020-06-18 & 44.784069   & 308.85        & 2.459019e+06 & 6942.0 & 17.107753 & HAT-P-67b\_OUT\_3\_after2  & 09:04:15 \\
    2020-06-18 & 44.782920   & 308.85        & 2.459019e+06 & 6942.0 & 17.107820 & HAT-P-67b\_OUT\_3\_after2  & 09:09:56 \\
    2020-06-18 & 44.781739   & 308.85        & 2.459019e+06 & 6942.0 & 17.107881 & HAT-P-67b\_OUT\_3\_after2  & 09:15:37 \\
    \bottomrule
\end{tabular}

>>>>

The sky fiber and target fiber have slightly different throughputs and illumination properties so the sky fiber must be scaled prior to subtraction from the target spectrum.  On average the target fiber sees $93\%$ of the flux of the sky reference fiber, and in detail this ratio depends on wavelength.  We quantified the wavelength dependence by acquiring calibration observations of blank sky in both the target and sky fiber.  We applied this wavelength-based scale factor to each target spectrum's associated reference sky fiber to achieve near-imperceptible sky-line residuals.  A few lines exhibit residuals which may arise from slight differences in the local atmospheric conditions between the target and sky fiber.

We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.  We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A}.

We flatten the spectral to continuum indices near the He 10830 features and compute the equivalent width (EW) defined over the spectral region \censorbox{xx,xxx}$-$\censorbox{xx,xxx} shown in Figure \censorbox{XX}.

The sky-subtraction, telluric masking, barycentric correction, and all of our other standard pre-processing steps are implemented in a new open-source Python interface \texttt{muler}\footnote{\url{https://github.com/OttoStruve/muler/}} (Gully-Santiago \emph{et al.}, submitted).

\subsection{EW Uncertainty quantification with MCMC}
We assessed the uncertainty in our equivalent fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}. The model consists of a straight-line trend with a Gaussian absorption line.  It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.

@@

@@

\input{tables/ew_table.tex}
